---
title: "Analysis for Tschanz et al. 2022 J Appl Ecol"
author: "Philippe Tschanz, Stefan Vogel, Achim Walter, Thomas Keller, Matthias Albrecht"
output:
  github_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

# Preliminaries

## Load libraries, settings, and functions

```{r}
library(here)
library(tidyverse)
library(sf)
library(MuMIn)
library(MASS)
library(pscl)
library(ggpubr)
library(lme4)
library(arm)
library(ggeffects)

select <- dplyr::select  # because MASS overrides dplyr function 'select'

## final figures, tables, and models are saved into lists
tables <- list()
figures <- list()
modlist <- list()

## defining global settings of parameters (for consistency)
parm <- list()
parm$col_2cat <- c("#0073C2FF", "#CD534CFF")
parm$shp_2cat <- c(16, 15)
parm$lab_sqa_cov_bare <- expression(Bare~ground~("%"))
parm$lab_soil_rel_dens <- expression(Relative~soil~bulk~density)
parm$lab_soil_ph <- expression(Soil~pH)
parm$lab_soil_sand <- expression(Sand~content~("%"))
parm$lab_lsc_dist_to_BPA <- "Distance to nearest BPA (m)"
parm$lab_lsc_BPA_500m <- "%BPA in 500 m radius"

## knitr settings
knitr::opts_chunk$set(
  echo = TRUE,
  dev = c("png", "pdf"))

## load custom functions
source(here("scripts", "functions.R"))
```


## Load data sets

```{r}
d.soil <- read_rds(here("data", "soil.rds"))
d.veg <- read_rds(here("data", "vegetation.rds"))
d.nest <- read_rds(here("data", "nests.rds"))
d.spec <- read_rds(here("data", "species.rds"))
d.field <- read_rds(here("data", "field_level_data.rds"))
sf.fields <- st_read(here("data", "geodata.gpkg"), layer = "fields")
```



# Materials and methods
Analysis for results reported in the *Materials and methods* section.

## Shortest distance between fields

What is the shortest distance (in m) that the fields are apart?
```{r}
index <- st_nearest_feature(sf.fields)
dist <- st_distance(sf.fields, sf.fields[index,], by_element = TRUE)
min(dist)
```





# Results
Analysis for the results, figures, and tables reported in the *Results* section following the same outline as in the manuscript.

## Nest density and species diversity in winter cereal fields

### Nest density

Number of fields with nest presence (1) and without nest presence (0) across both sampling rounds:
```{r}
table(d.field$pooled$nest_pa)
```

Range, standard deviation, and mean nest density, summed over both sampling rounds, within fields per $400 m^2$ sampling area, i.e., the number of nests counted within the eight $50\times 1m$ belt transects:
```{r}
density_400m2 <- d.field$pooled$nest_n
print(paste0("Mean (nests per 400m2): ", mean(density_400m2)))
print(paste0("Range (nests per 400m2): ", min(density_400m2), "-", max(density_400m2)))
print(paste0("SD (nests per 400m2): ", sd(density_400m2)))
```

Same but expressed per hectare:
```{r}
density_ha <- d.field$pooled$nest_n / 400 * 100 * 100
print(paste0("Mean (nests per ha): ", mean(density_ha)))
print(paste0("Range (nests per ha): ", min(density_ha), "-", max(density_ha)))
print(paste0("SD (nests per ha): ", sd(density_ha)))
```

Proportion of installed traps (in %) that captured the nesting female:
```{r}
dat <- table(d.nest$trap_outcome)
print(paste0("Capture rate (%): ", round(dat[c("Success")] / (dat[c("Fail")] + dat[c("Success")]) * 100, 2)))
```



### Species diversity
The data of the following tables are shown combined in Table 1.

Number of individuals per species captured within the $400m^2$ sampling area (CT = conventionally tilled, NT = no-till) of the 25 fields used for analysis:
```{r}
d.nest %>%
  filter(!is.na(nest_species)) %>%
  group_by(nest_species, mngt_soil, .drop = FALSE) %>%
  summarize(n = n()) %>%
  pivot_wider(c(nest_species), names_from = c(mngt_soil), values_from = n)
```

Number of individuals per species captured in the conventionally tilled field that was excluded from the analysis because of its much later sowing date compared to all other fields and consequently almost no vegetation cover, but still providing interesting insights:
```{r}
d.spec %>%
  filter(field == "JaPo02") %>%
  group_by(nest_species, mngt_soil, .drop = FALSE) %>%
  summarize(n = n()) %>%
  pivot_wider(c(nest_species), names_from = c(mngt_soil), values_from = n)
```

Number of individuals per species captured from incidentally found nests inside fields but outside the $400m^2$ sampling area:
```{r}
d.spec %>%
  filter(transect == "Outside") %>%
  group_by(nest_species, mngt_soil, .drop = FALSE) %>%
  summarize(n = n()) %>%
  pivot_wider(c(nest_species), names_from = c(mngt_soil), values_from = n)
```

Number of individuals per species captured from incidentally found nests inside fields but outside the $400m^2$ sampling area:
```{r}
d.spec %>%
  filter(transect == "PlowFurrow") %>%
  group_by(nest_species, mngt_soil, .drop = FALSE) %>%
  summarize(n = n()) %>%
  pivot_wider(c(nest_species), names_from = c(mngt_soil), values_from = n)
```





## Effects of tillage system on nesting

### Nesting incidence (nest presence / absence)
The model without interaction between tillage system and sampling round and without sampling round as explanatory variable performs best in terms of AICc. Neither the interaction between tillage system and sampling round nor the sampling round are significant. Thus, the final model included only tillage system. Table shown in Supplementary Information as Table S2.
```{r}
mod1 <- glm(
  nest_pa ~ mngt_soil * run,
  data = d.field$per_run,
  family = binomial(link = "logit"))

mod2 <- glm(
  nest_pa ~ mngt_soil + run,
  data = d.field$per_run,
  family = binomial(link = "logit"))

drop1(mod1, test = "Chisq")
drop1(mod2, test = "Chisq")
```

Tillage has no significant effect on nesting incidence in the final model:
```{r}
modlist$tilsys_inc$data <- d.field$pooled
modlist$tilsys_inc$model <- glm(
  nest_pa ~ mngt_soil,
  data = d.field$pooled,
  family = binomial(link = "logit"))
drop1(modlist$tilsys_inc$model, test = "Chisq")
```



### Nesting abundance

To test the effects of tillage system on nest abundance, we used a negative binomial model to account for overdispersion. Based on AIC, no zero-inflation modelling approach is necessary and the negative binomial model performed best.
```{r}
modlist$tilsys_abu$data <- d.field$pooled
dat <- modlist$tilsys_abu$data

# poisson
mod.p <- glm(
  nest_n ~ mngt_soil, data = dat, family = poisson(link = "log"))
# negative binomial
mod.nb <- glm.nb(
  nest_n ~ mngt_soil, data = dat)
# zero-inflated poisson
mod.zip <- zeroinfl(
  nest_n ~ mngt_soil | mngt_soil, data = dat, dist = "poisson", link = "logit") 
# zero-inflated negative binomial
mod.zinb <- zeroinfl(
  nest_n ~ mngt_soil | mngt_soil, data = dat, dist = "negbin", link = "logit") 
# hurdle poisson
mod.hp <- hurdle(
  nest_n ~ mngt_soil | mngt_soil, data = dat, dist = "poisson", link = "logit") 
# hurdle negative binomial
mod.hnb <- hurdle(
  nest_n ~ mngt_soil | mngt_soil, data = dat, dist = "negbin", link = "logit") 

# model fit comparison
AIC(mod.p, mod.nb, mod.zip, mod.zinb, mod.hp, mod.hnb) %>% arrange(AIC)
```

Neither the interaction between sampling round and tillage system nor the sampling round had a significant effect on tillage system, thus only tillage system was included. Table shown in Supplementary Information as Table S2.
```{r}
mod1 <- glm.nb(nest_n ~ mngt_soil * run, data = d.field$per_run)
mod2 <- glm.nb(nest_n ~ mngt_soil + run, data = d.field$per_run)

drop1(mod1, test = "Chisq")
drop1(mod2, test = "Chisq")
```

Tillage has no significant effect on nest abundance in the final model:
```{r}
modlist$tilsys_abu$data <- d.field$pooled
modlist$tilsys_abu$model <- glm.nb(
  nest_n ~ mngt_soil, data = modlist$tilsys_abu$data)

# p-value for tillage effect
drop1(modlist$tilsys_abu$model, test = "Chisq")

# 95% confidence interval using profile likelihood
confint(modlist$tilsys_abu$model)
```

Compute mean and 95% confidence interval for the number of nests for no-till and conventionally tilled fields, backtransformed to the scale of the response:
```{r}
# predict mean and 95% on scale of response
eff <- ggpredict(modlist$tilsys_abu$model)

newdat <- data.frame(
  mngt_soil = factor(c("CT", "NT"),
                     levels = c("CT", "NT"),
                     labels = c("Tillage", "No-till")))
newdat$fit <- eff$mngt_soil$predicted
newdat$lwr <- eff$mngt_soil$conf.low
newdat$upr <- eff$mngt_soil$conf.high
newdat
```


Same but converted to number of nests per hectare:
```{r}
newdat$fit / 400 * 100 * 100
```

Create plot with mean number of nests per tillage system and their 95% CI:
```{r}
dat <- d.field$pooled %>%
  mutate(mngt_soil = factor(
    mngt_soil, levels = c("CT", "NT"), labels = c("Tillage", "No-till")))

set.seed(36)
pos_dodge <- 0.75
colors <- parm$col_2cat
shapes <- parm$shp_2cat

figures$fig_1 <- ggplot(
  mapping = aes(x = mngt_soil, fill = mngt_soil,
             color = mngt_soil)) +
  # add points jittered
  geom_jitter(
    data = dat,
    mapping = aes(y = nest_n, shape = culture), 
    width = 0.25,
    size = 1.9, alpha = 0.4) +
  # add mean
  geom_point(
    data = newdat,
    mapping = aes(y = fit),
    size = 4) +
  # add 95% CI
  geom_errorbar(
    data = newdat,
    mapping = aes(ymax = upr, ymin = lwr),
    position = position_dodge(pos_dodge),
    width = 0, size = 1) +
  # style settings
  scale_fill_manual(values = colors, guide = "none") +
  scale_color_manual(values = colors, guide = "none") +
  scale_shape_manual(values= shapes, guide = "none") +
  scale_y_continuous(
    breaks = seq(0, 100, 2),
    sec.axis = sec_axis(
      trans = ~ .x * 25,
      breaks = seq(0, 400, 50),
      name = expression("Nests" ~ "per" ~ "hectare"))) +
  pt_theme() +
  labs(
    y = expression("Nests" ~ "per" ~ 400 ~ m^2 ~ "plot area"),
    x = NULL)
```





## Effects of distance from field edge on nest density

Create new data set for analysis containing the number of nests per field and transect. For the distance, we use the middle of the transect (e.g., the 0-1 m transect uses 0.5 m) for computation:
```{r}
# prepare data
modlist$dist$data <- d.nest %>%
  count(field, transect, .drop = FALSE, name = "nest_n") %>%
  mutate(
    dist_m = as.numeric(word(transect, sep = "\\-")) + 0.5,
    dist_m.log10 = log10(dist_m)) %>%
  left_join(., select(d.field$pooled, field, mngt_soil), by = "field")
```

For the discussion: what is the proportion (in %) of nests found on tramlines (`tramline` = yes) for each transects?
```{r}
tab <- table(d.nest$tramline, d.nest$transect)
round(prop.table(tab, margin = 2) * 100, 0)
```

Including tillage system does not improve model fit. Number of nests better described with an exponential decline relationship, which is used as final model. Results reported in Table S3 in the Supplementary Information.
```{r}
mod.dist <- glmer.nb(nest_n ~ scale(dist_m) + (1|field), data =  modlist$dist$data)
mod.ldist <- glmer.nb(nest_n ~ scale(dist_m.log10) + (1|field), data =  modlist$dist$data)
mod.dist_till <- glmer.nb(nest_n ~ scale(dist_m)*mngt_soil + (1|field), data =  modlist$dist$data)
mod.ldist_till <- glmer.nb(nest_n ~ scale(dist_m.log10)*mngt_soil + (1|field), data =  modlist$dist$data)

AICc(mod.dist, mod.ldist, mod.dist_till, mod.ldist_till) %>% arrange(AICc)

modlist$dist$model <- mod.ldist # final model
```

Get estimates, confidence intervals, and p-values for Table 2.
```{r}
summary(modlist$dist$model)
confint(modlist$dist$model)
drop1(modlist$dist$model, test = "Chisq") # p-value from LRT test
```

Refit model without standardizing predictor to avoid backtransformation for plotting. Compute Bayesian 95% credible intervals based on 2000 random draws from the joint posterior distribution. Note that for the modelling, we used the middle of the transect as distance (e.g. 2-3 m transect uses 2.5 m as distance from field edge) but plot the error bars 0, 1, 2, ... m for nicer visualization.
```{r}
dat <- modlist$dist$data
mod <- glmer.nb(nest_n ~ dist_m.log10 + (1|field), data =  dat)

# get bayesian 95% credible interval
nsim <- 2000
newdat <- data.frame(dist_m = seq(0, 30, length.out = 200))
newdat$dist_m.log10 <- log10(newdat$dist_m)
bsim <- sim(mod, n.sim = nsim)
Xmat <- model.matrix(~dist_m.log10, data = newdat)
newdat$fit <- exp(Xmat %*% fixef(mod))
fitmat <- matrix(ncol = nsim, nrow = nrow(newdat))
for(i in 1:nsim) fitmat[,i] <- exp(Xmat %*% bsim@fixef[i,])
newdat$lwr <- apply(fitmat, 1, quantile, prob = 0.025)
newdat$upr <- apply(fitmat, 1, quantile, prob = 0.975)

# mean number of nests +- se per transect
dat_stats <- dat %>%
  group_by(dist_m) %>%
  summarize(
    .groups = "drop",
    n = n(),
    mean = mean(nest_n),
    se = sd(nest_n) / sqrt(n),
    upr = mean + se,
    lwr = mean - se)

# figure 2
figures$fig_2 <- ggplot() +
    # error bars based on raw data
    geom_point(
      data = dat_stats,
      aes(y = mean, x = dist_m-0.5),
      size = 2.5) +
    geom_errorbar(
      data = dat_stats,
      aes(ymax = upr, ymin = lwr, x = dist_m-0.5),
      width = 0.2, size = 0.5) + 
    # model fit
    geom_line(
      data = newdat,
      aes(y = fit, x = dist_m),
      size = 1) +
    geom_ribbon(
      data = newdat,
      aes(ymin = lwr, ymax = upr, x = dist_m), alpha = .3) +
    # visualization settings
    scale_x_continuous(breaks = c(0, 1:2, 5, 10, 15, 20, 30)) +
    coord_cartesian(ylim = c(0, 1.5)) +
    pt_theme() +
    theme(legend.position = c(0.85, 0.9)) +
    labs(
      y = expression("Nests" ~ "per" ~ "transect" ~ "(mean" ~ "\u00B1" ~ "SE)"),
      x = "Distance from field edge (m)")
```




## Vegetation cover, soil properties and landscape context driving nesting

### Effects of vegetation cover on nesting incidence

Effects of bare soil cover on nest presence/absence at the 10x10 cm and the 1x1m scale. Only bare soil cover was used due to high collinearity with other cover variables.
```{r}
# 10 cm2 plots
modlist$veg_10cm$data <- d.veg %>%
  filter(scale == "10cm") %>%
  select(nest_pa, field, sqa_cov_bare) %>%
  mutate(sqa_cov_bare.z = as.numeric(scale(sqa_cov_bare)))

# 1 m2 plots
modlist$veg_1m$data <- d.veg %>%
  filter(scale == "1m") %>%
  select(nest_pa, field, sqa_cov_bare) %>%
  mutate(sqa_cov_bare.z = as.numeric(scale(sqa_cov_bare)))
```

```{r}
modlist$veg_10cm$model <- glmer(
  nest_pa ~ sqa_cov_bare.z + (1|field),
  data = modlist$veg_10cm$data,
  family = binomial(link = "logit"),
  na.action = na.fail,
  glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))

modlist$veg_1m$model <- glmer(
  nest_pa ~ sqa_cov_bare.z + (1|field),
  data = modlist$veg_1m$data,
  family = binomial(link = "logit"),
  na.action = na.fail,
  glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
```

Model output as reported in Table 2 for the 10 cm scale:
```{r}
summary(modlist$veg_10cm$model)
drop1(modlist$veg_10cm$model, test = "Chisq")
confint(modlist$veg_10cm$model)
```

Model output as reported in Table 2 for the 1m scale:
```{r}
summary(modlist$veg_1m$model)
drop1(modlist$veg_1m$model, test = "Chisq")
confint(modlist$veg_1m$model)
```

Create Fig. 3 combining results from both scales and compute 95% Bayesian credible intervals:
```{r}
# get 95% credible intervals (1m scale)
modlist$veg_1m$newdata <- pt_get_effects.glmm_pa(
  data = modlist$veg_1m$data,
  model = modlist$veg_1m$model,
  var_x = "sqa_cov_bare.z")

# get 95% credible intervals (10cm scale)
modlist$veg_10cm$newdata <- pt_get_effects.glmm_pa(
  data = modlist$veg_10cm$data,
  model = modlist$veg_10cm$model,
  var_x = "sqa_cov_bare.z")

figures$fig_3a <- pt_plot_effects.pa.2scales(
  dat_1m = modlist$veg_1m$data,
  dat_10cm = modlist$veg_10cm$data,
  newdat_1m = modlist$veg_1m$newdata,
  newdat_10cm = modlist$veg_10cm$newdata,
  var_x = "sqa_cov_bare.z",
  lab_x = parm$lab_sqa_cov_bare,
  pval_10cm = "paste(italic(beta), \" = 1.78 [1.37, 2.24], \", italic(p), \" < 0.001\")",
  pval_1m = "paste(italic(beta), \" = 1.23 [0.86, 1.65], \", italic(p), \" < 0.001\")")
```



### Effects of soil properties on nesting incidence

Fit full model with selected soil variables (based on biological reasoning and to avoid collinearity issues):
```{r}
modlist$soil$data <- d.soil %>%
  mutate(
    soil_rel_dens.z = scale(soil_rel_dens),
    soil_ph.z = scale(soil_ph),
    soil_sand.z = scale(soil_sand))

modlist$soil$mod_full <- glmer(
  formula = nest_pa ~ soil_rel_dens.z + soil_ph.z + soil_sand.z + (1|field),
  data = modlist$soil$data,
  family = binomial(link = "logit"), na.action = na.fail,
  glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
```

Identify and show best models (AICc < 2):
```{r}
modlist$soil$mod_set <- dredge(modlist$soil$mod_full)
modlist$soil$mod_top <- get.models(modlist$soil$mod_set, subset = delta < 2)
model.sel(modlist$soil$mod_top)
```

Model averaged summary of top models (AICc < 2):
```{r}
modlist$soil$mod_avg <- model.avg(modlist$soil$mod_top)
summary(modlist$soil$mod_avg)
```

95% confidence intervals (conditional):
```{r}
confint(modlist$soil$mod_avg, full = FALSE)
```

Variable importance:
```{r}
sw(modlist$soil$mod_avg)
```

Show all in nicely formatted table
```{r}
pt_get_tab_mod_avg(modlist$soil$mod_avg, type = "cond.avg")
```

Figure 3b-d:
```{r}
dat <- modlist$soil$data
mod <- modlist$soil$mod_top

# 3b) relative soil bulk density
var <- "soil_rel_dens.z"
newdat <- pt_get_effects.MuMIn_pa(dat, mod, var, "cond.avg")
figures$fig_3b <- pt_plot_effects.pa(
  data = dat,
  newdata = newdat,
  var_x = var,
  lab_x = parm$lab_soil_rel_dens,
  lab_stats = "paste(italic(beta), \" = 0.53 [0.11, 0.95], \", italic(p), \" = 0.014\")",
  sign = TRUE,
  breaks = seq(0, 1, .05))

# 3c) sand content
var <- "soil_sand.z"
newdat <- pt_get_effects.MuMIn_pa(dat, mod, var, "cond.avg")
figures$fig_3c <- pt_plot_effects.pa(
  data = dat,
  newdata = newdat,
  var_x = var,
  lab_x = parm$lab_soil_sand,
  lab_stats = "paste(italic(beta), \" = 0.34 [-0.02, 0.71], \", italic(p), \" = 0.067\")",
  sign = FALSE)

# 3d) soil ph
var <- "soil_ph.z"
newdat <- pt_get_effects.MuMIn_pa(dat, mod, var, "cond.avg")
figures$fig_3d <- pt_plot_effects.pa(
  data = dat,
  newdata = newdat,
  var_x = var,
  lab_x = parm$lab_soil_ph,
  lab_stats = "paste(italic(beta), \" = 0.12 [-0.24, 0.48], \", italic(p), \" = 0.511\")",
  sign = FALSE)
```





### Effects of landscape context (and other drivers) on nest abundance

```{r fig.height=10, fig.width=10}
modlist$abu$data <- d.field$pooled %>%
  mutate(
    soil_rel_dens.z = as.numeric(scale(soil_rel_dens)),
    soil_sand.z = as.numeric(scale(soil_sand)),
    sqa_cov_bare.z = as.numeric(scale(sqa_cov_bare)),
    lsc_Grassland_500m.z = as.numeric(scale(lsc_Grassland_500m)),
    lsc_Crop_500m.z = as.numeric(scale(lsc_Crop_500m)),
    lsc_BPA_500m.z = as.numeric(scale(lsc_BPA_500m)),
    lsc_dist_to_BPA.z = as.numeric(scale(lsc_dist_to_BPA)))
```

Fit full model:
```{r}
sel_vars <- c(
  "soil_rel_dens.z", "soil_sand.z", "sqa_cov_bare.z", "lsc_Grassland_500m.z",
  "lsc_Crop_500m.z", "lsc_BPA_500m.z", "lsc_dist_to_BPA.z")

modlist$abu$mod_full <- glm.nb(
  formula = as.formula(paste0("nest_n ~ ", paste0(sel_vars, collapse = " + "))),
  data = modlist$abu$data, na.action = na.fail)
```

Identify and show set of best models (AICc < 1.5):
```{r}
modlist$abu$mod_set <- dredge(modlist$abu$mod_full)
modlist$abu$mod_top <- get.models(modlist$abu$mod_set, subset = delta < 1.5)
model.sel(modlist$abu$mod_top)
```

Model averaged summary:
```{r}
modlist$abu$mod_avg <- model.avg(modlist$abu$mod_top)
summary(modlist$abu$mod_avg)
```

95% confidence interval (conditiona):
```{r}
confint(modlist$abu$mod_avg, full = FALSE)
```

Variable importance:
```{r}
sw(modlist$abu$mod_avg)
```

Results shown in nicely formatted table:
```{r}
modlist$abu$mod_tab <- pt_get_tab_mod_avg(modlist$abu$mod_avg, type = "cond.avg")
modlist$abu$mod_tab
```

Fig 4a-e
```{r}
# plots
dat <- modlist$abu$data
mod <- modlist$abu$mod_avg

# 4a) bare ground cover
var <- "sqa_cov_bare.z"; lab <- parm$lab_sqa_cov_bare
newdat <- pt_get_effects.glm(data = dat, model = mod, link = "log", var_x = var)
figures$fig_4a <- pt_plot_effects.n(
  data = dat, 
  newdata = newdat, 
  var_x = var,
  lab_x = lab,
  lab_stats = "paste(italic(beta), \" = 0.73 [0.23, 1.23], \", italic(p), \" = 0.004\")",
  sign = TRUE)

# 4b) relative soil bulk density
var <- "soil_rel_dens.z"; lab <- parm$lab_soil_rel_dens
newdat <- pt_get_effects.glm(data = dat, model = mod, link = "log", var_x = var)
figures$fig_4b <- pt_plot_effects.n(
  data = dat, 
  newdata = newdat, 
  var_x = var,
  lab_x = lab,
  lab_stats = "paste(italic(beta), \" = 0.45 [-0.04, 0.93], \", italic(p), \" = 0.071\")",
  sign = FALSE)

# 4c) sand content
var <- "soil_sand.z"; lab <- parm$lab_soil_sand
newdat <- pt_get_effects.glm(data = dat, model = mod, link = "log", var_x = var)
figures$fig_4c <- pt_plot_effects.n(
  data = dat, 
  newdata = newdat, 
  var_x = var,
  lab_x = lab,
  lab_stats = "paste(italic(beta), \" = 0.38 [-0.07, 0.83], \", italic(p), \" = 0.097\")",
  sign = FALSE,
  breaks = seq(0, 100, 5))

# 4d) BPA
var <- "lsc_BPA_500m.z"; lab <- parm$lab_lsc_BPA_500m
newdat <- pt_get_effects.glm(data = dat, model = mod, link = "log", var_x = var)
figures$fig_4d <- pt_plot_effects.n(
  data = dat, 
  newdata = newdat, 
  var_x = var,
  lab_x = lab,
  lab_stats = "paste(italic(beta), \" = 0.38 [-0.06, 0.82], \", italic(p), \" = 0.092\")",
  sign = FALSE,
  breaks = seq(0, 20, 2))

# 4e) Distance to BPA
var <- "lsc_dist_to_BPA.z"; lab <- parm$lab_lsc_dist_to_BPA
newdat <- pt_get_effects.glm(data = dat, model = mod, link = "log", var_x = var)
figures$fig_4e <- pt_plot_effects.n(
  data = dat, 
  newdata = newdat, 
  var_x = var,
  lab_x = lab,
  lab_stats = "paste(italic(beta), \" = -0.50 [-1.04, 0.04], \", italic(p), \" = 0.069\")",
  sign = FALSE,
  breaks = seq(0, 1000, 50))
```


# Figures



## Figure 1

```{r fig-1, fig.width=3.5, fig.height=3.5}
set.seed(36)
figures$fig_1
```



## Figure 2

```{r fig-2, fig.height = 3.5, fig.width = 5}
figures$fig_2
```



## Figure 3

```{r fig-3, fig.height=7, fig.width=8.5}
plotlist = figures[c("fig_3a", "fig_3b", "fig_3c", "fig_3d")]

ggarrange(
  labels = c("(a)", "(b)", "(c)", "(d)"),
  plotlist = plotlist, ncol = 2, nrow = 2)
```



## Figure 4

```{r fig-4, fig.height=6.5, fig.width=11}
plotlist = figures[c("fig_4a", "fig_4b", "fig_4c", "fig_4d", "fig_4e")]

ggarrange(
  figures$fig_4a, figures$fig_4b, figures$fig_4c, figures$fig_4d, figures$fig_4e, NULL,
  labels = c("(a)", "(b)", "(c)", "(d)", "(e)", ""),
  ncol = 3, nrow = 2)
```

