---
title: "Analysis for Supplementary Information to Tschanz et al. 2022 J Appl Ecol"
author: "Philippe Tschanz, Stefan Vogel, Achim Walter, Thomas Keller, Matthias Albrecht"
output:
  github_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

# Preliminaries

```{r}
library(iNEXT)
library(soiltexture)
library(tidyverse)
library(here)
library(ggpubr)
library(sf)
library(tmap)
library(lme4)
library(lmerTest)

# knitr settings
knitr::opts_chunk$set(
  echo = TRUE,
  dev = c("png", "pdf"))

# lists to save results
modlist <- list()
figures <- list()
tables <- list()

# load custom functions
source(here("scripts", "functions.R"))
```

## Load data sets
```{r}
d.nest <- read_rds(here("data", "nests.rds"))
d.spec <- read_rds(here("data", "species.rds"))
d.field <- read_rds(here("data", "field_level_data.rds"))
d.veg <- read_rds(here("data", "vegetation.rds"))

sf.fields <- st_read(here("data", "geodata.gpkg"), layer = "fields")
sf.plots <- st_read(here("data", "geodata.gpkg"), layer = "plots")
sf.plots_buf_500m <- st_read(here("data", "geodata.gpkg"), layer = "plots_buf_500m")
sf.landscape <- st_read(here("data", "geodata.gpkg"), layer = "landscape")
sf.bpa <- st_read(here("data", "geodata.gpkg"), layer = "bpa")
```





# Supplementary analysis

## Species diversity

We aggregated the bee data over both sampling rounds and per soil management treatment. Thus, we have $N=2$ assemblages (NT and CT).

Create a list for each soil management type that contains a vector of the species and their abundance.
```{r}
# no-till
ibad_nt <- d.nest %>%
  filter(mngt_soil == "NT", nest_species != "Unknown") %>%
  group_by(nest_species) %>%
  summarize(n = n(), .groups = "drop")

# conventional tillage
ibad_ct <- d.nest %>%
  filter(mngt_soil == "CT", nest_species != "Unknown") %>%
  group_by(nest_species) %>%
  summarize(n = n(), .groups = "drop")

# merged as list with nice names that are used for plotting
modlist$spec$ibad <- list(
  `Tillage` = as.numeric(ibad_ct$n),
  `No-till` = as.numeric(ibad_nt$n))

ibad_nt; ibad_ct
```

We now compute interpolated and extrapolated Hill curves. Note that "For species richness, the size in the R/E curve can be extrapolated to at most double or triple the minimum observed sample size, guided by an estimated asymptote. For Shannon diversity and Simpson diversity, if the data are not too sparse, the extrapolation can be reliably extended to infinity to attain the estimated asymptote provided in Chao et al. (2014).

We therefore compute Hill curves extrapolated to up to three times the minimum sample size.
```{r}
# define iNEXT settings
pt_iNEXT <- function(data, q){
  iNEXT(
    data, datatype = "abundance",
    q = q, nboot = 200, conf = 0.95, knots = 100,
    endpoint = min(sapply(data, sum)) * 3)
}

# compute Hill numbers
modlist$spec$inext <- list()
modlist$spec$inext$q0 <- pt_iNEXT(modlist$spec$ibad, 0)
modlist$spec$inext$q1 <- pt_iNEXT(modlist$spec$ibad, 1)
modlist$spec$inext$q2 <- pt_iNEXT(modlist$spec$ibad, 2)

modlist$spec$inext$all <- pt_iNEXT(modlist$spec$ibad, c(0,1,2))
```

Create figures for different diversity indices:
```{r}
lab_div_q0 <- expression("Species richness"~"("*italic(q)~"="~0*")")
lab_div_q1 <- expression("Shannon diversity"~"("*italic(q)~"="~1*")")
lab_div_q2 <- expression("Simpson diversity"~"("*italic(q)~"="~2*")")

figures$fig_s7a <- pt_plot_inext(modlist$spec$inext$q0, lab_div_q0)
figures$fig_s7b <- pt_plot_inext(modlist$spec$inext$q1, lab_div_q1)
figures$fig_s7c <- pt_plot_inext(modlist$spec$inext$q2, lab_div_q2)
```

Compute estimated species richness (Table S4).
```{r}
chao <- list()

chao$p0 <- ChaoRichness(modlist$spec$ibad, datatype = "abundance") %>%
  mutate(type = "Species richness")
chao$p1 <- ChaoShannon(modlist$spec$ibad, datatype = "abundance") %>%
  mutate(type = "Shannon diversity") %>%
  rename(Est_s.e. = Est_s.e)
chao$p2 <- ChaoSimpson(modlist$spec$ibad, datatype = "abundance") %>%
  mutate(type = "Simpson diversity")

tables$tab_s4 <- bind_rows(chao) %>%
  mutate(
    mngt_soil = rep(names(modlist$spec$ibad), 3),
    Observed = sprintf("%.2f", Observed),
    Estimator = sprintf("%.2f", Estimator),
    CI = paste0("[", sprintf("%.2f", `95% Lower`), ", ", sprintf("%.2f", `95% Upper`), "]")) %>%
  select(type, mngt_soil, Observed, Estimator, CI)
colnames(tables$tab_s4) <- c("Diversity measure", "Soil management", "Observed", "Estimate", "95% CI")
rownames(tables$tab_s4) <- 1:6
```


## Effect of bare ground cover on nesting incidence and potential confounding with distance from field edge

### Effects of distance form field edge on proportion of bare ground

The distance from field edge was not recorded for vegetation control plots but is available for nest plots because the nest id is known. We use this data to test for potential effect of distance from field edge on proportion of bare ground using a linear mixed-effect model with proportion of bare ground as response variable and distance from field edge as explanatory variable. Field was included as random intercept and slope.

Need to add information on distance from field edge to vegetation data:
```{r}
add <- d.nest %>%
  select(nest_id, transect)

# 1m2 scale
d.veg_1m <- d.veg %>%
  left_join(., add, by = "nest_id") %>%
  filter(scale == "1m") %>%
  select(nest_pa, field, transect, sqa_cov_bare) %>%
  mutate(sqa_cov_bare.z = as.numeric(scale(sqa_cov_bare))) %>%
  mutate(dist_m = as.numeric(word(transect, sep = "\\-")))

# 10cm2 scale
d.veg_10cm <- d.veg %>%
  left_join(., add, by = "nest_id") %>%
  filter(scale == "10cm") %>%
  select(nest_pa, field, transect, sqa_cov_bare) %>%
  mutate(sqa_cov_bare.z = as.numeric(scale(sqa_cov_bare))) %>%
  mutate(dist_m = as.numeric(word(transect, sep = "\\-")))
```

No significant effect of distance from field edge on proportion of bare ground at the 1m2 scale:
```{r}
dat <- filter(d.veg_1m, nest_pa == 1, dist_m >= 0)
mod <- lmer(
  sqa_cov_bare ~ dist_m + (dist_m|field),
  data = dat,
  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
summary(mod, ddf = "Kenward-Roger")
```

No significant effect of distance from field edge on proportion of bare ground at the 10cm2 scale:

```{r}
dat <- filter(d.veg_10cm, nest_pa == 1, dist_m >= 0)
mod <- lmer(
  sqa_cov_bare ~ dist_m + (dist_m|field),
  data = dat,
  control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
summary(mod, ddf = "Kenward-Roger")
```

### Effects of proportion of bare ground on nesting excluding data from the two transects closest to field edges

The following analyses are identical to the ones in the main manuscript testing for effects of proportion of bare ground on nesting incidence but excluding data from the two transects closest to field edges to verify the robustness of the strong effect found in the main manuscript.

Strong effect of proportion of bare ground on nesting incidence at the 1m2 scale:
```{r}
dat <- filter(d.veg_1m, dist_m >= 2 | is.na(dist_m))
mod <- glmer(
  nest_pa ~ sqa_cov_bare.z + (1|field),
  data = dat,
  family = binomial(link = "logit"),
  na.action = na.fail,
  glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
summary(mod)
drop1(mod, test = "Chisq")
confint(mod)
```

Strong effect of proportion of bare ground on nesting incidence at the 10cm2 scale:
```{r}
dat <- filter(d.veg_10cm, dist_m >= 2 | is.na(dist_m))
mod <- glmer(
  nest_pa ~ sqa_cov_bare.z + (1|field),
  data = dat,
  family = binomial(link = "logit"),
  na.action = na.fail,
  glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
summary(mod)
drop1(mod, test = "Chisq")
confint(mod)
```



# Supplementary figures


## Figures S4-5

Maps showing landscape data within 500m buffer.
```{r}
# clip landscape data to 500m buffer
sf.bpa_clip <- st_intersection(sf.bpa, sf.plots_buf_500m)
sf.lct_clip <- st_intersection(sf.landscape, sf.plots_buf_500m)

# for nicer plots
plots_buf_outer <- st_buffer(sf.plots_buf_500m, 30) %>%
  mutate(mngt_soil = factor(mngt_soil, levels = c("NT", "CT"), labels = c("No-till", "Tillage")))
plots_buf_inner <- sf.plots_buf_500m
```


```{r}
# 500m buffer
map_buffer <- tm_shape(
  plots_buf_outer,
  is.master = TRUE,
  unit = "m") +
  tm_fill(
    col = "mngt_soil",
    palette = c("blue", "red"),
    title = "Tillage system") +
  tm_facets(by = c("field"), ncol = 7) + 
  tm_shape(plots_buf_inner) +
    tm_fill(
      col = "white")

# 50x30m study plots
map_plots <- tm_shape(sf.plots) +
  tm_fill(
    col = "black",
    alpha = 1)

# field boundaries
map_fields <- tm_shape(sf.fields) +
  tm_borders(
    col = "black",
    lwd = 2)

# general style settings
style <- tm_layout(
  legend.title.fontface = 2,
  legend.outside.size = 0.15,
  panel.label.size = 1.5,
  inner.margins = c(0.15,0,0,0) + 0.03)

# scale bar
scale_bar <- tm_scale_bar(breaks = c(0, 250, 500), text.size = 1)
```

```{r fig-s4, fig.height=9, fig.width=8}
col_lct <- c("#af3700", "#f5d45e", "#227744", "#3CDB84", "#ff996a", "#d2d2d2", "#b40f52", "#55c2ff", "#96dcf2")

# crop, forest, grassland, other, urban, water, wetland
col_lct <- c("#f5d45e", "#227744", "#3CDB84", "#ff996a", "#939393", "#55c2ff", "#96dcf2")

map_lct <- tm_shape(sf.lct_clip) +
  tm_fill(
    col = "class",
    title = "Landscape",
    palette = col_lct,
    alpha = 0.8) +
  tm_facets(by = c("field"), ncol = 5)

map_lct_final <- map_buffer + map_lct + map_fields + map_plots + style + scale_bar
map_lct_final
```

```{r fig-s5, fig.height=9, fig.width=8}
map_bpa <- tm_shape(sf.bpa_clip) +
  tm_fill(
    title = "Biodiversity Promotional Area",
    col = "#00cc03") +
  tm_facets(by = c("field"), ncol = 5)

map_bpa_final <- map_buffer + map_bpa + map_fields + map_plots + style + scale_bar
map_bpa_final
```

## Figure S6

Texture triangle showing mean soil texture per species. Note that one species is not shown (nest id `LuHe01_FIT_2.1`). The soil texture from this sample was very different from all other soil samples taken in the same field and its clay content (62%) unrealistic, likely reflecting some laboratory measurment error. This soil sample was also excluded for all analyses as mentioned in the main text.
```{r fig-s6, fig.height=8, fig.width=8}
# prepare data for soilTexture package
dat_tri <- d.spec %>%
  filter(
    !is.na(soil_sand), nest_species != "Unknown", nest_id != "LuHe01_FIT_2.1") %>%
  select(nest_species, soil_sand, soil_silt, soil_clay) %>%
  mutate(
    nest_species = factor(nest_species),
    genus = factor(gsub( " .*$", "", nest_species)))

# layout settings
pt.pch <- 1:20
css.names <- c("soil_clay","soil_silt","soil_sand")
pt.lwd <- 2; pt.cex <- 1.5; pt.col <- c("#0073C2FF", "#8F7700FF", "#CD534CFF")

# triangle plot
base <- TT.plot(
  tri.data = dat_tri,
  tri.sum.tst = FALSE,
  class.sys = "USDA.TT",
  css.names = c("soil_clay","soil_silt","soil_sand"),
  col = pt.col[dat_tri$genus],
  pch = pt.pch[dat_tri$nest_species], cex = pt.cex, lwd = pt.lwd,
  cex.axis = 1.3, font.axis = 1, lwd.axis = 3,
  arrows.show = FALSE,
  class.lab.show = "abr",
  main = "",
  new.mar = c(4, 0, 0, 0))

# to get rid of the arrow, but keep labels (arrows.show = F also removes labels...)
TT.axis.arrows(base, css.lab = c("Clay (%)", "Silt (%)", "Sand (%)"), a.l = c(0.15, 0.45),
    a.h.s = 0.95, a.t.s = 0.13,
    a.t.s2 = -0.0, a.b.s = 0,
    text.tol = NULL, text.sum = NULL, blr.clock = NULL,
    tlr.an = NULL, base.css.ps.lim = NULL, tri.sum.tst = FALSE,
    tri.pos.tst = FALSE, lwd.lab = NULL, arrows.lty = 0,
    col.lab = NULL, font.lab = NULL, cex.lab = NULL,
    family.op = NULL, unit.ps = NULL, unit.tx = NULL,
    lang = NULL)

# legend
legend(
  x = -10, y = 100,
  pch = pt.pch, col = c(rep(pt.col[1], 5), pt.col[2], rep(pt.col[3], 6)), pt.lwd = pt.lwd, pt.cex = pt.cex,
  bty = "n",
  legend = levels(dat_tri$nest_species), text.font = 3)
```


## Figure S7

Impact of tillage system on species diversity.
```{r fig-s7, fig.height=4, fig.width=11}
plotlist = figures[c("fig_s7a", "fig_s7b", "fig_s7c")]

ggarrange(
  plotlist = plotlist,
  labels = c("(a)", "(b)", "(c)"),
  common.legend = TRUE, nrow = 1)
```


# Supplementary tables

## Table S1

```{r table-s1}
dat <- d.field$pooled %>%
  select(
    mngt_soil,
    area_ha, alt_plot, slope_plot,
    lsc_BPA_500m, lsc_Forest_500m, lsc_Grassland_500m, lsc_Crop_500m, lsc_Urban_500m)

vars <- dat %>%
  select(-mngt_soil) %>%
  colnames()

# template to save results
table <- data.frame(
  variable = vars,
  summary_nt = NA,
  summary_ct = NA,
  t_stat = NA,
  t_df = NA,
  t_pval = NA,
  mwu_stat = NA,
  mwu_df = NA,
  mwu_pval = NA)

# loop over each variable
for(i in 1:length(vars)){
  var.i <- vars[[i]]
  dat.i <- dat[, c("mngt_soil", var.i)]
  
  # get summary statistics by variable and tillage system
  d.s <- dat.i %>%
    group_by(mngt_soil) %>%
    summarize(
      n = n(),
      mean = mean(.data[[var.i]]),
      min = min(.data[[var.i]]),
      max = max(.data[[var.i]]),
      sd = sd(.data[[var.i]]),
      se = sd / sqrt(n)) %>%
    mutate(
      pretty = paste0(
        sprintf("%.2f", mean), " \u00B1 ", sprintf("%.2f", se),
        " (", sprintf("%.2f", min), " - ", sprintf("%.2f", max), ")"))
  
  table$CT[i] <- filter(d.s, mngt_soil == "CT")$pretty
  table$NT[i] <- filter(d.s, mngt_soil == "NT")$pretty
  form.i <- as.formula(paste0(var.i, "~", "mngt_soil"))
  
  # t-test
  test_t <- t.test(form.i, data = dat.i, alternative = "two.sided")
  table$t_pval[i] <- ifelse(test_t$p.value < 0.001, "<0.001", sprintf("%.3f", test_t$p.value))
  table$t_stat[i] <- sprintf("%.2f", test_t$statistic)
  table$t_df[i] <- sprintf("%.2f", test_t$parameter)
  
  # mann-withney u test
  test_mwu <- wilcox.test(form.i, data = dat.i, exact = FALSE, alternative = "two.sided")
  table$mwu_pval[i] <- ifelse(test_mwu$p.value < 0.001, "<0.001", sprintf("%.3f", test_mwu$p.value))
  table$mwu_stat[i] <- sprintf("%.2f", test_t$statistic)
  table$mwu_df[i] <- sprintf("%.2f", test_t$parameter)
}

# create nicely formated table
table_pretty <- table %>%
  pivot_longer(cols = c(NT, CT), names_to = "tillage_system", values_to = "summary") %>%
  mutate(
    summary = paste0(tillage_system, ": ", summary)) %>%
  select(variable, summary, t_stat, t_df, t_pval, mwu_stat, mwu_df, mwu_pval)
table_pretty

#write_csv(table_pretty, file = here("table_s1.csv"))
```

## Table S2
See `analysis_manuscript.Rmd`

## Table S3
See `analysis_manuscript.Rmd`

